% !TEX root = Nidhal_Nouma.tex  

\documentclass[letterpaper,11pt]{article}
\usepackage{helvet}

\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\selectfont
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Nidhal Nouma}} & Email : \href{mailto:nidhal.nouma.0@gmail.com}{nidhal.nouma.0@gmail.com}\\
  \href{https://www.linkedin.com/in/nidhal-nouma/}{Linkedin.com/in/nidhal-nouma} & Mobile : +1 (813) 553-9103 \\\href{https://github.com/NidhalNouma}{github.com/NidhalNouma} 
  % & Lutz, FL
\end{tabular*}


%-----------Profile-----------------
\section*{Profile}

\begin{flushleft}
      {With six years of experience in software development and a strong passion for innovative solutions, I possess the skills necessary to create high-quality software applications. My proficiency in various programming languages, frameworks, and technologies enables me to deliver solutions that not only meet user expectations but also adhere to industry standards for security, performance, and maintainability. Additionally, my collaborative nature and ability to effectively communicate complex technical concepts to non-technical individuals make me a valuable asset to any development team.}
\end{flushleft}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Upwork}{}
      {Software Developer}{Mar 2021 - May 2023}
     \begin{itemize}
      \item
          {Optimized web applications and trading platform software for performance and scalability, resulting in improved response times and increased user engagement.} 
          
      \item
          { Developed custom trading algorithms and automated trading systems to improve trading performance and reduce risk.} 
          
      \item
          {Worked with traders and compliance teams to ensure software solutions comply with regulatory requirements and industry best practices.} 
          
      \item
          {Collaborated with third-party vendors to integrate their solutions into web applications and trading platforms, ensuring seamless user experience and functionality.} 
          
     \end{itemize}
    Click \href{https://www.upwork.com/freelancers/nidhalnouma}{\underline{here}} or visit the URL below to check my profile:\newline
    https://www.upwork.com/freelancers/nidhalnouma

 \resumeSubheading
      {Freelancer}{}
      {Software Developer}{Jul 2017 - Feb 2023}
     \begin{itemize}
      \item
          {Developed and maintained web applications using HTML, CSS, JavaScript, React, NextJs, Node.js, Express, MongoDB, MySQL, PHP, Python, Docker, AWS, google cloud, firebase, and more to meet or exceed user expectations.} 
          
      \item
          {Worked on the development of trading platform software that incorporates algorithmic trading, data analysis, and risk management features using a C++ extension.} 
          
      \item
          {Designed and implemented RESTful APIs to integrate third-party services into trading platforms and web applications.} 
          
      \item
          {Collaborated with cross-functional teams, including designers, project managers, and traders to ensure the delivery of high-quality and user-friendly software products.} 
          
      \item
          {Contributed to the development of web development and trading platform software best practices and helped mentor junior developers.} 
          
      \item
          {Stayed up-to-date with the latest trends and technologies in web development and trading platform software development to ensure the use of the most efficient and effective solutions.} 
          
     \end{itemize}
    Click \href{https://www.freelancer.com/u/nidhalnouma}{\underline{here}} or visit the URL below to check my profile:\newline
    https://www.freelancer.com/u/nidhalnouma


  \resumeSubHeadingListEnd
  
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Sousse}{Sousse, Tunisia}
      {Bachelor's degree in Electronics Engineering}{Sep. 2013 -- Jun. 2016}
    \resumeSubheading
      {Lycée 2 Mars 1934 }{Sousse, Tunisia}
      {High school diploma in Technical Science}{Sep. 2011 -- Jun. 2013}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
% \resumeSubHeadingListStart
 
\begin{itemize}
   \item{
     \textbf{Languages:}
     \newline{Javascript, TypeScript, Python, C++, PHP, Bash}
     \newline{Swift, Dart, MQL, Pinescript}
     \newline{SQL, NoSQL}
     \newline{HTML, Jinja, CSS, SCSS, SASS}
   }
   
   \item{
     \textbf{Technologies:}
     \newline{NodeJs, NextJs, ReactJs, ReduxJs, VueJs, chartJs, socket.io}
     \newline{Django, Flask, Laravel}
     \newline{Tailwindcss, Material-UI, Bootstrap, Bulma}
     \newline{MySQL, Postgress, MongoDB, DynamoDB, Firestore}
     \newline{RESTful API, GraphQL}
     \newline{Linux, Docker, CI/CD, Git}
     \newline{AWS, Google Cloud, Firebase, Vercel, Netlify, Heroku, Linode}
   }
\end{itemize}
 % \resumeSubHeadingListEnd

% -----------PROJECTS-----------------
\section{Selected projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://app.automatedtrader.com}{\underline{automatedtrader.com}}}
      {A website designed to automate notification alerts from the TradingView platform and send them to a broker for execution.}

    \resumeSubItem{\href{https://dojibot.com}{\underline{dojibot.com}}}
      {Website to gather subscriptions and keep track of the products.}
      
    \resumeSubItem{\href{https:talktime.us}{\underline{talktime.us}}}
      {Web app that randomly connects people through audio calls and gathers feedback from anonymous users.}
      
    \resumeSubItem{\href{https://looksyummyapp.com}{\underline{looksyummyapp.com}}}
      {I worked on the backend as well as mobile development of the "looksyummy" app. It is a social app designed for restaurants to share meals and plans.}
      
    \resumeSubItem{\href{https://handsfree.dominateforex.info}{\underline{dominateforex.info}}}
      {A basic website to collect subscriptions and sell digital products with an admin section.}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
